\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Drew M Altschul \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
35 Roberts Rd, Apt 1   & {\it E-mail:}  d.m.altschul@sms.ed.ac.uk\\            
Cambridge, MA  02138 & {\it Phone:} 617-448-0601 \\    
\end{tabular}

%\section{\sc Research Interests}
%Basis for altrusitic behavior in primates, between group interactions in primates, genetic diversity among primates and genetic impact on behavior, ontogeny of language

% \section{\sc Research Interests}
% Behavioral neuroscience, development of new technologies in neuroscience, neuroethology and relations to sociobiology, executive control and the prefrontal cortex, adult neurogenesis in the central nervous system, acoustic signal processing and analysis

\section{\sc Education}

{\bf Brandeis University}, Waltham, Massachusetts\\
\vspace*{-.1in}
\begin{list1}
\item[] M.S. Neuroscience, 2010
\vspace*{.05in}
%\item[] GPA: 4.5 (out of 5.0)
\end{list1}

{\bf Massachusetts Institute of Technology}, Cambridge, Massachusetts\\
%{\em Department of Brain and Cognitive Sciences} 
\vspace*{-.1in}
\begin{list1}
\item[] B.S. Brain and Cognitive Sciences, 2008
\vspace*{.05in}
%\item[] GPA: 4.5 (out of 5.0)
\end{list1}

%\section{\sc Relevant Coursework}
%\begin{list1}
%\item[] Animal Behavior
%\vspace*{.05in}
%\item[] Brain Structure and its Origins
%\vspace*{.05in}
%\item[] Cellular Neuroscience (Graduate)
%\vspace*{.05in}
%\item[] Computational Neuroscience
%\vspace*{.05in}
%\item[] Developmental Neurobiology (Graduate)
%\vspace*{.05in}
%\item[] Microcomputer Project Laboratory
%\vspace*{.05in}
%\item[] Sensation and Perception
%\vspace*{.05in}
%\item[] Systems Neuroscience (Graduate)

%\end{list1}



\section{\sc Research Experience}

{\bf Columbia University}, New York, NY

\vspace{-.3cm}
{\em Lab Manager}, with Prof. Herbert S. Terrace \hfill {\bf June 2010 - present}\\
\vspace{-.5cm}

Manage all aspects of short and long term lab activities, including the design and implementation of research, writing articles, protocols, and presentations, animal handling and management, data analysis, recruiting students and volunteers, and coordinating their duties and projects in the lab.

\vspace{-.1cm}

{\bf Cognitive Ethology Research Group/Baboon Research Unit}, Cape Town, South Africa

\vspace{-.3cm}
{\em Field Assistant}, with Dr. Rahel Noser \hfill {\bf September 2009 - April 2010}\\
\vspace{-.5cm}

Worked with a multinational research group to collect data from free ranging baboons surrounding Cape Town in order construct solutions to problems with baboon-human conflict in the region. Everyday work included design and execution of playback experiments, recording animal vocalizations, GPS tracking of foraging patterns, and behavioral and population scanning of entire troops.

\vspace{-.1cm}

{\bf Brandeis University}, Waltham, MA

\vspace{-.3cm}
{\em Rotation Student} \hfill {\bf August 2008 - May 2009}\\
\vspace{-.5cm}

Practiced behavioral, systems, and cellular neurobiology techniques, developed novel experiments and methods, analyzed behavioral and physiological data. 

\vspace{-.1cm}

{\bf Massachusetts Institute of Technology}, Cambridge, MA

\vspace{-.3cm}
{\em Research Assistant}, with Prof. Earl Miller \hfill {\bf May 2006 - May 2008}\\
\vspace{-.5cm}

Work included animal handling, behavioral training, task design and data analysis, MRI analysis, electrode array construction and subsequent recording.

\vspace{-.1cm}

{\bf Willamette University}, Salem, OR

\vspace{-.3cm}
{\em Research Assistant}, with Dr. Jeff Willemsen \hfill {\bf May 2003 - August 2003}\\
\vspace{-.5cm}

Interned in an organic chemistry research lab, where I performed chemical syntheses of various compounds in the cyclophane family of organic molecules. 

\section{\sc Teaching Experience}

{\bf Massachusetts Institute of Technology}, Cambridge, MA

\vspace{-.3cm}
{\em Teaching Assistant} for Animal Behavior \hfill {\bf September 2007 - January 2008}\\
\vspace{-.5cm}

Served as the students' individual gateway to understanding course material. Duties included grading assignments, writing assignments and quizzes, advising students on term paper topics and research, and being accessible to students.



\vspace{.3cm}

\section{\sc Skills} 
\begin{list2}
\item Programming/Scripting Languages: proficient with Python, R, C, REALbasic, Scheme, and \LaTeX, familiar with Java, JavaScript, HTML, XML, PHP, Basic, MySQL and Pascal
\item Computer Applications: MATLAB, LabVIEW, SPSS, Adobe Creative Suite, Microsoft Office or equivalent
\item Operating Systems: Windows, Linux/Unix, Mac OS X
\item IT: multipurpose server administration, computer hardware assembly and upkeep
\item Electrical Engineering: analog, digital, and power electronics circuit design, soldering, and wiring
\item Audio Engineering: recording, editing, and analysis in the studio and field for use in scientific, musical, and audiobook projects
\item Over-the-Air Radio Engineering: 3 years experience in live broadcasting
\item Animal Handling: 2 years handling and behavioral training of rhesus macaques, plus additional exposure to rats, ferrets, and wild primates. Responsibilites have included training the animals in complex visual and motor tasks and transporting them to and from housing on a daily basis
\item Graphic Design: iPhone app icon and layout design, website design consultation

\vspace{.3cm}
\end{list2}

\section{\sc Publications} 

Jensen, G., Altschul, D., Danly, E., Terrace, H.S. (2013) Rhesus macaques use a common representation space to solve distinct problems. {\it PLoS One.}

Jensen, G., Altschul, D., Terrace, H. (2013). Monkeys would rather see and do: preference for agentic control in rhesus macaques. {\it Experimental Brain Research}, 1-14.

Avdagic, E., Jensen, G., Altschul, D., Terrace, H. (2013) Rapid Cognitive Flexibility of Rhesus Macaques Performing Psychophysical TaskSwitching. {\it Manuscript submitted for publication.}

Morgan, V., Altschul, D.M., Terrace H.S., (2013) Strategic and graduated metacognitive judgments by monkeys.  {\it Manuscript submitted for publication.}

% Altschul, D.M., Ward, D.P., Jensen, G., Terrace, H.S. (2012) Natural, artistic, and numerical concept formation in monkeys. {\it Manuscript in preparation.}


\end{resume}
\end{document}




